### 2023-01-18 paper.tex
Feedback for Section IV

	As has been described in Section~\ref{sec:intro}, we opted to support Solidity in the repository, since Solidity is the most established programming languages for smart contracts today~\cite{soliditycheck}. We keep the option open to add further languages like Vyper or Yul if they find a wider distribution in the future.

	In order to follow the best practices for creating a repository, a number of approaches for collecting datasets were studied. One of the best examples of preparing a large scale dataset from GitHub repositories can be found in \cite{thestack}. In the area of smart contracts, repositories can be found in the works of \cite{ren}, \cite{ferreirarepo} and others. Similar to these datasets, our repository should contain the source code of all available contracts. Apart from the source files themselves, additional features need to be incorporated through the storage of metadata about the smart contracts, in order to provide researchers with complete information and to reduce the amount of pre-processing required before analyzing the code in the repository. Also, multiple versions of the source code, if available, can be used to compare incremental changes to the gas consumption and also to detect the introduction to vulnerabilities through changes in the source code. The metadata may include the name of the contract, a description of what it is intended for, details about the source repository, the compiler versions used to generate the bytecodes and also the commit messages, which can be helpful in manual annotation of changes. As mentioned in \cite{thestack}, the repository creation procedure should take into account repository licenses, particularly if the repository is to be made publicly available. The repository should be able to filter out files without permissive licenses.

	The repository needs to be stored in a database along with an appropriate database management system (DBMS) that can enable easy and efficient querying capabilities. For this purpose, SQL databases such as SQLite, MySQL or NoSQL databases such as MongoDB can be used.  The smart contracts should be searchable using their metadata, names, also the language used and the corresponding compiler versions. A general purpose relational DBMS or an off-the-shelf document retrieval system operating on a NoSQL database provides ready deep and optimized querying capabilities while ensuring scalability and extendability to newer fields that can be added to the database.

>>>>

	As has been described in Section~\ref{sec:intro}, we opted to support Solidity in the repository, since Solidity is the most established programming languages for smart contracts today~\cite{soliditycheck}. We keep the option open to add further languages like Vyper or Yul, if they find a wider distribution in the future.

	In order to follow the best practices for creating a repository, a number of approaches for collecting datasets were studied. One of the best examples of preparing a large scale dataset from GitHub repositories can be found in \cite{thestack}. In the area of smart contracts, repositories can be found in the works of \cite{ren},\todo{Broken reference} \cite{ferreirarepo} and others. Similar to these datasets, our repository should contain the source code of all available contracts. Apart from the source files themselves, additional features need to be incorporated through the storage of metadata about the smart contracts, in order to provide researchers with complete information and to reduce the amount of pre-processing required before analyzing the code in the repository. Also, multiple versions of the source code, if available, can be used to compare incremental changes to the gas consumption and also to detect the introduction to vulnerabilities through changes in the source code. The metadata may include the name of the contract, a description of what it is intended for, details about the source repository, the compiler versions used to generate the bytecodes and also the commit messages, which can be helpful in manual annotation of changes. As mentioned in \cite{thestack}, the repository creation procedure should take into account repository licenses, particularly if the repository is to be made publicly available. The repository should be able to filter out files without permissive licenses.

	The repository needs to be stored in a database along with an appropriate database management system (DBMS) that can enable easy and efficient querying capabilities. For this purpose, SQL databases such as SQLite, MySQL or NoSQL databases such as MongoDB can be used.  The smart contracts should be searchable using their metadata, names, the language used, and the corresponding compiler versions. A general purpose relational DBMS or an off-the-shelf document retrieval system operating on a NoSQL database provides ready deep and optimized querying capabilities while ensuring scalability and extendability to newer fields that can be added to the database.

	\todo{As discussed today, and also mentioned above: I am clearly missing a discussion of the need for the script. The reviewers will not understand why it is needed. We need a paragraph on this, clearly giving this information.}
